A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-11-29 writeup/revision 1/paper.tex

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{table*}
\scriptsize
\begin{center}
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi & 0.635 (296) & \textbf{0.695} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil & \textbf{0.653} (273) ** & 0.250 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
Malayalam & 0.764 (234) & \textbf{0.827} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
Spanish & 0.814 (191) & \textbf{0.837} (18) & US (122) Mexico (16) Spain (14)  & India (15) New Zealand (1) Brazil (1) \\
French & 0.750 (170) & \textbf{0.816} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
Chinese & \textbf{0.601} (116) & 0.552 (21) & US (75) Singapore (13) China (9)  & Hong Kong (6) Australia (3) Germany (2)  \\
German & \textbf{0.825} (91) & 0.768 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
Italian & \textbf{0.863} (90) * & 0.796 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
Amharic & \textbf{0.136} (16) ** & 0.009 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
Kannada & 0.704 (105) & NA (0) & India (105)  & \\
Arabic & \textbf{0.741} (60) ** & 0.604 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
Portuguese & 0.869 (101) & \textbf{0.963} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
Turkish & 0.759 (76) & \textbf{0.804} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
Telugu & \textbf{0.799} (102) & 0.500 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
Irish & \textbf{0.742} (54) & 0.709 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
Swedish & \textbf{0.734} (54) & 0.711 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
Czech & \textbf{0.706} (45) * & 0.612 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
Russian & \textbf{0.146} (67) * & 0.119 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
Breton & 0.167 (3) & \textbf{0.178} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
\hline\hline
\end{tabular}
\normalsize
\end{center}
\caption{Translation quality when partitioning the translations into two groups, one containing translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other containing translations from Turkers outside those regions. In general, in-region Turkers provide higher quality translations. (*) indicates differences significant at p=0.05, (**) at p=0.10.} \label{region-summary}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
\centering
\scriptsize
\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
\hline
workers & quality & speed & \\\hline
%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
%&&slow& ar ga he pa sv tr\\\cline{2-4}
%& low or medium &fast& hi mr ta ur \\\cline{3-4}
%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}   Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
& low or  &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
&medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, UKranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
&low or  &fast&--\\\cline{3-4}
&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
\end{tabular}
\caption{The green box shows the languages which we have found most supported by MTurk in terms of worker population, worker ability, and speed of completion. Languages have ``many'' workers if we recorded more than 50 active in-region Turkers. Languages are ``high'' quality if they average greater than 70\% accuracy on our controls. Languages are ``fast'' if all of our translations (approx. 10,000 words each) were completed within two weeks.}
\label{recommendations}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{table*}
\scriptsize
\begin{center}
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi & 0.635 (296) & \textbf{0.695} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil & \textbf{0.653} (273) ** & 0.250 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
Malayalam & 0.764 (234) & \textbf{0.827} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
Spanish & 0.814 (191) & \textbf{0.837} (18) & US (122) Mexico (16) Spain (14)  & India (15) New Zealand (1) Brazil (1) \\
French & 0.750 (170) & \textbf{0.816} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
Chinese & \textbf{0.601} (116) & 0.552 (21) & US (75) Singapore (13) China (9)  & Hong Kong (6) Australia (3) Germany (2)  \\
German & \textbf{0.825} (91) & 0.768 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
Italian & \textbf{0.863} (90) * & 0.796 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
Amharic & \textbf{0.136} (16) ** & 0.009 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
Kannada & 0.704 (105) & NA (0) & India (105)  & \\
Arabic & \textbf{0.741} (60) ** & 0.604 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
Portuguese & 0.869 (101) & \textbf{0.963} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
Turkish & 0.759 (76) & \textbf{0.804} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
Telugu & \textbf{0.799} (102) & 0.500 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
Irish & \textbf{0.742} (54) & 0.709 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
Swedish & \textbf{0.734} (54) & 0.711 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
Czech & \textbf{0.706} (45) * & 0.612 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
Russian & \textbf{0.146} (67) * & 0.119 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
Breton & 0.167 (3) & \textbf{0.178} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
\hline\hline
\end{tabular}
\normalsize
\end{center}
\caption{Translation quality when partitioning the translations into two groups, one containing translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other containing translations from Turkers outside those regions. In general, in-region Turkers provide higher quality translations. (**) indicates differences significant at p=0.05, (*) at p=0.10.} \label{region-summary}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\paragraph{Validation of controls} 
%Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.27), suggesting that some control translations have already been indexed by Google. We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.
%
%As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.  We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz. }  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.  In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.  
%
%We ranked the 24 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.  The Pearson correlation was $\rho=0.53$.  We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.    
%
%Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\centering
\small
\footnotesize
\begin{tabular}{|p{.1\linewidth}|p{.1\linewidth}|p{.1\linewidth}|p{0.5\linewidth}|}
\hline
\footnotesize workers & \footnotesize  quality & \footnotesize speed & \\\hline
%many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5} de es fr gu it kn ml nl pt ro sr te tl \\\cline{3-4}
%&&slow& ar ga he pa sv tr\\\cline{2-4}
%& low or medium &fast& hi mr ta ur \\\cline{3-4}
%&&slow&bn bo bpy ceb ne new pl ru sd zh\\\cline{1-4}
many &high&fast&\cellcolor[rgb]{0.5, 0.8, 0.5}    Dutch, French, German, Gujarati, Italian, Kannada, Malayalam, Portuguese, Romanian, Serbian, Spanish, Tagalog, Telugu \\\cline{3-4}
&&slow& Arabic,  Hebrew, Irish, Punjabi, Swedish, Turkish\\\cline{2-4}
& low or  &fast& Hindi, Marathi, Tamil, Urdu \\\cline{3-4}
&medium&slow&Bengali,  Bishnupriya Manipuri, Cebuano,  Chinese, Nepali, Newar, Polish, Russian, Sindhi, Tibetan\\\cline{1-4}
few &high  &fast& Bosnia, Croatian  Macedonian  Malay  Serbo-Croatian\\\cline{3-4}
&&slow&Afrikaans, Albanian, Aragonese, Asturian, Basque, Belarusian, Bulgarian, Central Bicolano, Czech, Danish, Finnish, Galacian, Greek, Haitian, Hungarian, Icelandic, Ilokano, Indonesian, Japanese, Javanese, Kapampangan, Kazakh, Korean, Lithuanian, Low Saxon, Malagasy, Norwegian (Bokmal), Sicilian, Slovak, Slovenian, Thai, UKranian, Uzbek, Waray-Waray, West Frisian, Yoruba\\\cline{2-4}
&low or  &fast&--\\\cline{3-4}
&medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}Amharic,  Armenian, Azerbaijani, Breton, Catalan, Georgian, Latvian, Luxembourgish, Neapolitian, Norwegian (Nynorsk), Pashto, Piedmontese, Somali, Sudanese, Swahili, Tatar, Vietnamese, Walloon, Welsh \\\hline
none&low or medium&slow&\cellcolor[rgb]{0.8, 0.5, 0.5}  Esperanto, Ido, Kurdish, Persian, Quechua, Wolof, Zazaki\\\hline
\end{tabular}
\normalsize
\caption{The green box shows the best languages to target on MTurk. These languages have many workers who generate high quality results quickly. We defined {\it many} workers as 50 or more active in-region workers, {\it high} quality as $\geq$70\% accuracy on the gold standard controls, and {\it fast} if all of the 10,000 words were completed within two weeks.}
\label{recommendations}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
